### 2009-04-06 talk/icooolps2009-dotnet/conclusion.tex
Typos.

The \emph{Dynamic Language Runtime}\footnote{\texttt{http://www.codeplex.com/dlr}}
(DLR) is a library designed to ease the implementation of dynamic languages
for .NET: IronPython is based on the DLR, so the same remarks apply.

>>>>

The \emph{Dynamic Language Runtime}\footnote{\texttt{http://www.codeplex.com/dlr}}
(DLR) is a library designed to ease the implementation of dynamic languages
for .NET: the DLR is closely related to IronPython\footnote{In fact, the DLR
  started as a spin-off of IronPython, and nowadays the latter is based on the
  former.} and employs the techniques described above; thus, the remarks
about the differences between PyPy and IronPython apply to all DLR based
languages.
